\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{\Large{Abbas Rangwala}} \\
\indent Bhavnagar (Gujarat, INDIA) - 364001\\
\indent email id : \textbf{abbastrick@gmail.com} \\
\indent GitHub Profile : \textbf{github.com/abba5} \\
\indent Linkedin Profile : \textbf{linkedin.com/in/abba5} \\
\indent Mobile No.: \textbf{+91 7600475292} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\
% \begin{table}[ht!]
\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University} & \textbf{Year} & \textbf{CPI/\%} \\
\hline
%Post Graduate Specialization:\,\, & \textit{Computer Science and Engineering} \\
%Post Graduation & IIT Bombay  & 2014 & 8.0 \\
UnderGraduate Specialization: & \textit{Electronic \& Communication Engineering} \\
Graduation & Dharmsinh Desai University, Nadiad  & 2016-2020  & 8.3\\
Class XII (H.S.C.) & GSHSEB & 2016 & 81\% \\
Class X (S.S.C.) & GSEB & 2014 & 84\% \\ 
\hline
\end{tabular}
\end{center}
% \end{table}

\resheading{\textbf{ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}\itemsep \isep
\item \noindent Selected for ICPC Regional 2019. (Team Name :- "Last\_Segment\_Tree", rank :- 313)
\item \noindent  Finalist (137th) in CodeGladiator 2019
\item \noindent Rated \textbf{5 Star} Coder on Codechef. (Codechef handle is:- "abba5")
\item \noindent Specialist on Codeforces. (Codeforces handle is :- "abba5")
\item \noindent  Qualified for Semi Finals in E-Yantra Robotics Competition 2017
\end{itemize}

\resheading{\textbf{INDUSTRY EXPERIENCE} }\\[\lsep]

\begin{itemize}\itemsep \isep

\item \noindent \textbf{Status} 1.5+ Years of experience.

\item \noindent \textbf{Swiggy} (Backend Software Engineer) \\\emph{(Feb '21 - Current)} \\[-0.6cm]
\begin{itemize}\itemsep \isep
\item \noindent Working on user facing services which control all pages of Swiggy Food Application.
\end{itemize}

\item \noindent \textbf{Knowledge Foundry} (Backend Software Engineer) \\\emph{(May '20 - Feb '21)} \\[-0.6cm]
\begin{itemize}\itemsep \isep
\item \noindent Working on a Generic Product Life cycle Management software. Built for Food and Beverage industry, the system currently supports managing products right from their inception till market availability, comparison of products based on constituent ingredients and nutrients.
\item \noindent Working on Spark SQL to analysing data.
\item \noindent Technologies:  Node JS, Neo4j Graph Database, ElasticSearch, Spark, Hadoop
\end{itemize}
\item \noindent \textbf{Meditab Software (India) Pvt. Ltd.} (Software Engineer Intern) \\\emph{(Dec'19 - Apr'20)} \\[-0.6cm]
\begin{itemize}\itemsep \isep
\item \noindent Design scheduling software for Vial Automation (Drug Filling System), which will manage all component in Vial Automation.
\item \noindent Technologies: CherryPy, Peewee. 
\end{itemize}
\end{itemize}

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}\itemsep \isep
\item \noindent Algorithms and Data Structures
\item \noindent Operating System
\item \noindent Mathematics
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}\itemsep \isep
\item \noindent \textbf{Programming Languages: } C, C++, Scala, Java, Golang
\item \noindent \textbf{Scripting Languages: } Python, Shell, JavaScript, TypeScript
\item \noindent \textbf{Software Tools: } Git, \LaTeX, Octave, Scilab
\item \noindent \textbf{Cloud Technologies: } AWS, Kubernetes
\\
\\
\end{itemize}

\resheading{\textbf{MAJOR PROJECTS } }\\[\lsep]
\begin{itemize}

\item \textbf{Glob-Poster} (Learning Advanced Web Technologies) \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : Basic social media page where people can post there thought.
	\item Front-end logic was developed using React and designed using Next JS and Chakra UI 
	\item Back-end logic was developed using Node.js  with MySQL as Database and graphQL as query language. Redis use to store the user session.
	\end{itemize}


\item \textbf{Ant Colony Optimization on TSP} (Project for learning purpose) \\
\emph{(July'19 - Dec'19)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective : Find Near-optimal solution for TSP using ant colony optimization.
	\item Programming Language: C++
	\end{itemize}

\item \textbf{FPGA Based Crypto-System} (Project for learning AES and FPGA) \\
\emph{(Jan'19 - April'19)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective :Built a module which can be used in any application for encryption/ decryption of data.
	\item AES-128 as symmetric key and RSA as asymmetric key. 
	\item Altera DE1 FPGA Board for verification of code. 
	\end{itemize}
	
\item \textbf{Spotter Snake
} (Hardware project developed for E-Yantra Robotics Competition 2017
) \\
 \emph{(Nov'17 - Feb'18)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective: To make a robot similar to snake which can travel through different terrains.
	\item Whole hardware structure was designed in Fusion 360 and modeled using V-REP and then 3D printed.
	\item The movement of the snakes was controlled by Arduino Nano using a Wireless Remote and multiple servos.
	\end{itemize}

% \item \textbf{Variable Dual Voltage Power Supplier
% } (Project for learning purpose) \\
%  \emph{(Dec'17 - Feb'18)} \\[-0.6cm]
% 	\begin{itemize}\itemsep \isep
%     \item Objective : To give bias voltage to an Op-amp ($\pm$12 - 0 ).
% 	\item Voltage Regulate part designed by discrete element.  
% 	\end{itemize}
	
\end{itemize}


\resheading{\textbf{EXTRACURRICULAR ACTIVITY} }\\[\lsep]
\begin{itemize}\itemsep \isep
    \item \textbf{Chairperson of IEEE, DDU Student Branch}\emph{ (Dec'18 - Dec'19)}
    \item \textbf{Student Ambassador for IEEEXterem }\emph{(July'19 - Dec'19)}
    \item \textbf{Problem setter at IEEE DDU SB Programming Competition} 
    \emph{(23$^{rd}$ Jan 2019)}
    
\end{itemize}



\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}\itemsep \isep
\item \noindent Gaining knowledge in irrespective domain.
\item \noindent Volunteer Work.
\item \noindent Gaming
\end{itemize}



\indent I hereby acknowledge that the information provided above is correct and best of my knowledge.\\

\end{document}
